Meta-analysis

### 2019-09-15 05_MetaAnalysis.Rmd
Update 05_MetaAnalysis.Rmd
This DOES knit, however it needs to be thorougly checked and validated against Paul's original work to be sure that we're getting what we want. Some models do fail to converge. Need to address that.

- Use graphs in place of tables

- Spelling corrections

- Import data and format cols correctly

- Put line breaks in text for easier Git commit tracking

---
title: "Meta-analysis"
author: "P. Melloy"
date: "04/07/2019"
output: html_document
---

```{r MEsummary_Libraries}
library(tidyverse)
library(kableExtra)
library(leaflet)
```

@@

## Data-wrangling

```{r Meta_dataImport, message=FALSE}
PM_MB_means <-
   read_csv(
      "data/1902 powdery mildew-Mungbean - Collated means.csv"
   )

@@

## Investigating data and the number of factors represented in each trial

@@

```{r Fungicides}
PM_MB_means %>%
   group_by(fungicide_ai, trial_ref) %>%
   summarise() %>%
   count(sort = TRUE) %>%
   rename(Trials = n) %>%
   kable()

# How many trials do we have if Tebe and Propi are pooled?

Tebuconazole and propiconazole might be able to be pooled as a 'triazole' fungicide treatment. 
Amistar Xtra is a combination of azoxystrobin and cyproconazole.
Custodia is a combination of tebuconazole and azoxystrobin.
Perhaps Amistar Xtra and Custodia might be able to be pooled given they both contain strobilurin and triazole, however they contain differing dose ratios (inverted).

@@

```{r Tebe_dose}
PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole") %>%
   select(trial_ref,
          year,
          location,
          first_sign_disease,
          dose_ai.ha,
          total_fungicide) %>%
   kable()
```

@@

Some experiments were designed to investigate the effect of row spacing and plant density on powdery mildew disease and crop yield.
The results showed that the row spacing had no statistically significant effect on powdery mildew, but narrower rows did increase yield significantly.
Seven trials used a row spacing of 0.75 meters.

```{r row_spacing.m}
PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole") %>%
   group_by(row_spacing.m, trial_ref) %>%
   summarise() %>%
   count() %>%
   rename(Trials = n) %>%
   kable()

PM_MB_means %>%
   filter(fungicide_ai == "propiconazole") %>%
   group_by(row_spacing.m, trial_ref) %>%
   summarise() %>%
   count() %>%
   rename(Trials = n) %>%
   kable()

PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole",
         row_spacing.m == 0.75) 
```

@@

```{r Host_genotype}
PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole",
         row_spacing.m == 0.75) %>%
   group_by(host_genotype, trial_ref) %>%
   summarise() %>%
   count() %>%
   rename(Treatments = n) %>%
   kable()
```
In general the mungbean varieties have the following resistance to powdery mildew.  
   - Berken: Highly susceptible  
   - Crystal: Susceptible  
   - Jade: Moderately susceptible

@@

```{r variance}
PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole",
         row_spacing.m == 0.75) %>%
   group_by(trial_ref, location, y_error.type) %>%
   summarise(tebu_treatments = length(y_error.type))

PM_MB_means %>%
   filter(fungicide_ai == "propiconazole",
          row_spacing.m == 0.75) %>%
   group_by(trial_ref, location, y_error.type) %>%
   summarise(Tebe_Treatments = length(y_error.type))
colnames(PM_MB_means)
```

```{r LSD_trials}
Trials <- PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole",
          row_spacing.m == 0.75,
          y_error.type == "lsd (P=0.05)") %>%
   select(trial_ref) %>%
   distinct()
```

The trial, `mung1112/02` uses Least square differences to describe the variation within the experiment.
The following code attempts to convert this to sampling variance as per the method in [Nugugi et.al (2011)](https://apsjournals.apsnet.org/doi/10.1094/PHYTO-08-10-0221).
Ideas for using a T-critical value of 1.697 came from reading a [statisics-how-to website](https://www.statisticshowto.datasciencecentral.com/how-to-calculate-the-least-significant-difference-lsd/).
A [table of T-critical values](https://www.statisticshowto.datasciencecentral.com/tables/t-distribution-table/) was consulted where 30 degrees of freedom within experiment was used to find the 'T-crit' value of 1.697.

![Calculating sampling variance from mean squared error Paul et. al. (2008)](Paul_etal_2008.PNG)

@@

# calculate the Sampling variance from the standard deviation
# standard error of the mean equals the standard deviation divided by the square root of the number of samples
# Sv <- sem^2 <- stdev/sqrt(n)
# Sampling variance eqauls the square of the standard error.
# Sv <- (stdev/sqrt(n))^2

@@

Now for the trickier part creating 'Sampling Variance' for treatments where only mean yield is recorded.  
The trial which does not report any type of variance also reports that there is no significant difference between the means.
```{r}
NATrials <- PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole",
          row_spacing.m == 0.75,
          is.na(y_error.type)) %>%
   select(trial_ref) %>%
   distinct()
```

A single trial `mung1516/03` within the current scope of the meta-analysis fails to report a variance statistic. According to [Machado F. et. al (2017)](http://apsjournals.apsnet.org/doi/10.1094/PDIS-03-17-0340-RE) [Paul et. al. (2007)](https://apsjournals.apsnet.org/doi/pdfplus/10.1094/PHYTO-97-2-0211) uses linear regression model to estimate sampling variance.

```{r na2Sampling_variance}
library(lme4)
library(scales)

@@

# Run a linear model with grain_yield.t.ha as a fixed effect predictor and trial as a random intercept
PM_MB_trianLMER <- lmer(yield_error ~ grain_yield.t.ha +
                           (1 | trial_ref), data = PM_MB_train)
summary(PM_MB_trianLMER)

# grain yeild (in this model) IS a significant predictor for yeild error (t value = 5.826)
#  And the variance increases as the mean increases
# does log transformation improve the model?

PM_MB_trianLMER.1 <- lmer(log(yield_error) ~ `grain_yield.t.ha` +
                             (1 | trial_ref), data = PM_MB_train)
summary(PM_MB_trianLMER.1) # grain yeild a significant predictor of log(yeild error)
anova(PM_MB_trianLMER, PM_MB_trianLMER.1) # no significant difference between the models

PM_MB_trianLMER.2 <- lmer(yield_error ~ log(`grain_yield.t.ha`) +
                             (1 | trial_ref), data = PM_MB_train)
summary(PM_MB_trianLMER.2) # log(grain yeild) is a significant predictor of yeild error
anova(PM_MB_trianLMER, PM_MB_trianLMER.2) # no significant difference between the models

PM_MB_trianLMER.3 <-
   lmer(log(yield_error) ~ log(`grain_yield.t.ha`) +
           (1 | trial_ref),
        data = PM_MB_train)
summary(PM_MB_trianLMER.3) # log(grain yeild) is a significant predictor of log(yeild error)
anova(PM_MB_trianLMER, PM_MB_trianLMER.3) # no significant difference between the models

# Lets try with Fungicide as a fixed effect
PM_MB_trianLMER.4 <-
   lmer(yield_error ~ `grain_yield.t.ha` + as.factor(fungicide_ai) +
           (1 | trial_ref),
        data = PM_MB_train)
summary(PM_MB_trianLMER.4)
anova(PM_MB_trianLMER, PM_MB_trianLMER.4) # no significant difference between the models

#log transforming the response or predictor variables did not improve the model therefore I will leave it untransformed
# I will be using the first model PM_MB_trianLMER for further analyses beyond this point

# Extract the model cooeficients
paramA <-
   (summary(PM_MB_trianLMER)$coef)[2, 1] # Extract the overall mean Slope to predict Yield error
InterC <-
   (summary(PM_MB_trianLMER)$coef)[1, 1] # Extract the overall mean intercept to predict Yield error
lmer.coef <-
   coef(PM_MB_trianLMER) # extracting the mean random intercept for each of trial variables

# plot of the mixed effect model, Black line shows the mean lmer regression line
ggplot(PM_MB_train) +
   geom_point(aes(y = yield_error, x = `grain_yield.t.ha`, colour = trial_ref)) +
   geom_abline(
      intercept = c(InterC, lmer.coef$trial_ref[, 1]),
      slope = c(paramA, lmer.coef$trial_ref[, 2]),
      size = 1,
      colour = c("Black", hue_pal()(11))
   ) +
   coord_cartesian(xlim = c(0, 3))

```
```{r na2Sv_formula}

for (i in NATrials$trial_ref) {
   #Sv <- (log(PM_MB_means[PM_MB_means$trial_ref == i,]$`grain_yield.t.ha`) - InterC)/ paramA  # parameter from when I had the predictor and response variable flipped

@@

   PM_MB_means[PM_MB_means$trial_ref == i,]$yield_error <- Sv
   PM_MB_means[PM_MB_means$trial_ref == i,]$y_error.type <-
      "SamplingVariance"
}

@@

Lets look at the model without the trial mung1718/01, as it looks to be adding some skew.
```{r lmer_remove_mung1718-01}
# remove from mung1718/01 from training dataset
PM_MB_train.2 <-
   PM_MB_train[PM_MB_train$trial_ref != "mung1718/01",]

# Rerun the model
PM_MB_trianLMER.5 <- lmer(yield_error ~ `grain_yield.t.ha` +
                             (1 | trial_ref), data = PM_MB_train.2)
summary(PM_MB_trianLMER.5) # no significant effect of mean grain yield on yeild error

# Extract the cooeficients
paramA <-
   (summary(PM_MB_trianLMER.5)$coef)[2, 1] # Extract the overall mean Slope to predict Yield error
InterC <-
   (summary(PM_MB_trianLMER.5)$coef)[1, 1] # Extract the overall mean intercept to predict Yield error
lmer.coef <-
   coef(PM_MB_trianLMER.5) # extracting the mean random intercept for each of trial variables

# plot the data with the predicted slopes overlayed
ggplot(PM_MB_train.2) +
   geom_point(aes(y = yield_error, x = `grain_yield.t.ha`, colour = trial_ref)) +
   geom_abline(
      intercept = c(InterC, lmer.coef$trial_ref[, 1]),
      slope = c(paramA, lmer.coef$trial_ref[, 2]),
      size = 1,
      colour = c("Black", hue_pal()(10))
   ) +
   coord_cartesian(ylim = c(0, 0.33))

Just for kicks lets look at the linear regression model as a Random effects model where `grain_yield.t.ha` is set as a random slope to the random intercept `trial_ref`.  
The model fits better as shown by an ANOVA comparison. But how to impute from this model if mean variance for a trial is unknown....
```{r random_slope_model}

# Run a linear model with Yield error as a fixed effect predictor and Trial as a random intercept
PM_MB_trianLMERx <- lmer(yield_error ~ 1 +
                            (`grain_yield.t.ha` | trial_ref), data = PM_MB_train)

anova(PM_MB_trianLMER, PM_MB_trianLMERx) # random slope model NOT significantly better # P = 0.6677

summary(PM_MB_trianLMERx)

InterC <-
   (summary(PM_MB_trianLMER)$coef)[1, 1] # Extract the overall mean intercept

lmer.coefx <- coef(PM_MB_trianLMERx)

# plot of the mixed effect model, Black line shows the mean lmer regression line
ggplot(PM_MB_train) +
   geom_point(aes(y = yield_error, x = `grain_yield.t.ha`, colour = trial_ref)) +
   geom_abline(
      intercept = lmer.coefx$trial_ref[, 2],
      slope = lmer.coefx$trial_ref[, 1],
      size = 1,
      colour = hue_pal()(11)
   ) +
   coord_cartesian(xlim = c(0, 3),
                   ylim = c(0, 1))
```

After much deliberation I don't think this is possible to use the model with grain yield/ha as a random slope. Even though we know the grain yields and the mean in the grain yields we still can't predict the effect of the random intercept trial on the yield error.  
I also re-ran the model without including the trial which we used LSD to interpret the sampling variance and the model lost a lot of significance.

Emerson proposed I look at the between trial variation

PM_MB_means.SV <-
   PM_MB_means[PM_MB_means$y_error.type == "SamplingVariance", ]

PM_MB_means_T <- PM_MB_means %>%
   group_by(trial_ref) %>%
   summarise(
      trial_mean = mean(grain_yield.t.ha, na.rm = TRUE),
      BW_trial_variance = sd(grain_yield.t.ha, na.rm = TRUE) ^ 2
   )
PM_MB_means_T

All_Trials <- unique(PM_MB_means$trial_ref)
PM_MB_means$TrialVariance <- NA

for (i in All_Trials) {
   PM_MB_means[PM_MB_means$trial_ref == i, "TrialVariance"] <-
      PM_MB_means_T[PM_MB_means_T$trial_ref == i, "BW_trial_variance"]
}

PM_MB_means$TrialVariance

summary(lm(BW_trial_variance ~ trial_mean, data = PM_MB_means_T))
summary(lm(
   BW_trial_variance ~ trial_mean,
   data = subset(PM_MB_means_T, fungicide_ai == "tebuconazole")
))
summary(lm(
   BW_trial_variance ~ trial_mean,
   data = subset(PM_MB_means_T, fungicide_ai == "propiconazole")
))

plot(BW_trial_variance ~ trial_mean, data = PM_MB_means_T)
abline(-0.01356, 0.03076)

>>>>

---
title: "Meta-analysis"
author: "P. Melloy"
date: "`r Sys.Date()`"
output: html_document
---

```{r MEsummary_Libraries, message=FALSE}
library(tidyverse)
library(theme.usq)
```

@@

```{r data_import, message=FALSE, echo=FALSE}
PM_MB_means <-
   read_csv(
      "data/1902 powdery mildew-Mungbean - Collated means.csv"
   )

@@

## Visualise Data

Visualise and inspect the number of factors represented in each trial.

@@

```{r Fungicides}
PM_MB_means %>%
   group_by(fungicide_ai, trial_ref) %>%
   summarise() %>%
   count(sort = TRUE) %>%
   rename(Trials = n) %>%
   ggplot(aes(x = reorder(fungicide_ai, Trials), y = Trials)) +
   xlab("Fungicide active ingredient") +
   ylab("N Trials") +
   geom_col() +
   scale_fill_usq() +
   scale_colour_usq() +
   theme_usq() +
   coord_flip()
```

Tebuconazole and propiconazole might be able to be pooled as a triazole fungicide treatment. 
Amistar Xtra is a combination of azoxystrobin and cyproconazole.
Custodia is a combination of tebuconazole and azoxystrobin.
Amistar Xtra and Custodia might be able to be pooled given they both contain strobilurin and triazole, however, they contain differing dose ratios (inverted).

@@

```{r tebu_dose}
PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole") %>%
   select(trial_ref,
          year,
          location,
          first_sign_disease,
          dose_ai_f1_g.ha,
          total_fungicide) %>%
   ggplot(aes(x = as.factor(dose_ai_f1_g.ha))) +
   xlab("Dose (g ai/ha)") +
   geom_bar() +
   scale_fill_usq() +
   scale_colour_usq() +
   theme_usq()
```

@@

Some experiments were designed to investigate the effect of row spacing and plant density on powdery mildew disease.
The results showed that the row spacing had no statistically significant effect on powdery mildew, but narrower rows did increase yield significantly, which has been shown by Kerry McKenzie's work as well.
Eight trials used a row spacing of 0.75&nbsp;meters and tebuconazole as an active ingredient (AI).

```{r row_spacing.m}
PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole" | fungicide_ai == "propiconazole") %>%
   group_by(fungicide_ai, row_spacing.m, trial_ref) %>%
   summarise() %>%
   count() %>%
   rename(Trials = n) %>%
   ggplot(aes(x = as.factor(row_spacing.m), y = Trials)) +
   xlab("Row Spacing (m)") +
   ylab("N Trials") +
   ggtitle(label = "Trial row spacings using tebuconazole") +
   geom_col(aes(fill = fungicide_ai),
            position = "dodge") +
   scale_fill_usq(name = "Fungicide AI") +
   theme_usq()

PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole",
         row_spacing.m == 0.75) %>% 
   glimpse()
```

@@

```{r Host_genotype}
PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole",
         row_spacing.m == 0.75) %>%
   group_by(host_genotype, trial_ref) %>%
   summarise() %>%
   count() %>%
   rename(Treatments = n) %>%
   ggplot(aes(x = host_genotype, y = Treatments)) +
   xlab("Cultivar") +
   ylab("N Trials") +
   ggtitle(label = "Cultivars used in tebuconazole trials with 0.75 m row spacing") +
   geom_col() +
   scale_fill_usq() +
   scale_colour_usq() +
   theme_usq()
```

In general the mungbean varieties have the following resistance to powdery mildew.

   - Berken: Highly susceptible

   - Crystal: Susceptible

   - Jade: Moderately susceptible

@@

```{r variance}
# Trials using tebuconazole
PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole",
         row_spacing.m == 0.75) %>%
   group_by(trial_ref, location, y_error.type) %>%
   summarise(tebuconazole_trts = length(y_error.type))

# Trials using propiconazole
PM_MB_means %>%
   filter(fungicide_ai == "propiconazole",
          row_spacing.m == 0.75) %>%
   group_by(trial_ref, location, y_error.type) %>%
   summarise(propiconazole_trts = length(y_error.type))
```

```{r LSD_trials}
Trials <- PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole",
          row_spacing.m == 0.75,
          y_error.type == "lsd (P=0.05)") %>%
   select(trial_ref) %>%
   distinct()
Trials
```

The trial, `mung1112/02` uses Least Square Differences (LSD) to describe the variation within the experiment.
The following code attempts to convert this to sampling variance as per the method in [Nugugi et.al (2011)](https://apsjournals.apsnet.org/doi/10.1094/PHYTO-08-10-0221).
Ideas for using a T-critical value of 1.697 came from reading a [statisics-how-to website](https://www.statisticshowto.datasciencecentral.com/how-to-calculate-the-least-significant-difference-lsd/).
A [table of T-critical values](https://www.statisticshowto.datasciencecentral.com/tables/t-distribution-table/) was consulted where 30 degrees of freedom within experiment was used to find the 'T-crit' value of 1.697.

![Calculating sampling variance from mean squared error Paul et al. (2008)](Paul_etal_2008.PNG)

@@

# calculate the Sampling variance from the standard deviation
# standard error of the mean equals the standard deviation divided by the square root of the number of samples
# Sv <- sem^2 <- stdev/sqrt(n)
# Sampling variance equals the square of the standard error.
# Sv <- (stdev/sqrt(n))^2

@@

Now for the trickier part creating 'Sampling Variance' for treatments where only mean yield is recorded.  
The trial which does not report any type of variance also reports that there is no significant difference between the means.

```{r}
NATrials <- PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole",
          row_spacing.m == 0.75,
          is.na(y_error.type)) %>%
   select(trial_ref) %>%
   distinct()
```

A single trial `mung1516/03` within the current scope of the meta-analysis fails to report a variance statistic. According to [Machado F. et. al (2017)](http://apsjournals.apsnet.org/doi/10.1094/PDIS-03-17-0340-RE) [Paul et al. (2007)](https://apsjournals.apsnet.org/doi/pdfplus/10.1094/PHYTO-97-2-0211) uses linear regression model to estimate sampling variance.

```{r na2Sampling_variance, message=FALSE}
library(lme4)
library(scales)

@@

# Run a linear model with grain_yield.t.ha as a fixed effect predictor and trial as a random intercept
PM_MB_trainLMER <- lmer(yield_error ~ grain_yield.t.ha +
                           (1 | trial_ref), data = PM_MB_train)
summary(PM_MB_trainLMER)

# grain yield (in this model) IS a significant predictor for yield error
# (t value = 5.826)
# And the variance increases as the mean increases does log transformation
# improve the model?

PM_MB_trainLMER.1 <- lmer(log(yield_error) ~ `grain_yield.t.ha` +
                             (1 | trial_ref), data = PM_MB_train)
summary(PM_MB_trainLMER.1) # grain yield a significant predictor of log(yield error)
anova(PM_MB_trainLMER, PM_MB_trainLMER.1) # no significant difference between the models

PM_MB_trainLMER.2 <- lmer(yield_error ~ log(`grain_yield.t.ha`) +
                             (1 | trial_ref), data = PM_MB_train)
summary(PM_MB_trainLMER.2) # log(grain yeild) is a significant predictor of yield error
anova(PM_MB_trainLMER, PM_MB_trainLMER.2) # no significant difference between the models

PM_MB_trainLMER.3 <-
   lmer(log(yield_error) ~ log(`grain_yield.t.ha`) +
           (1 | trial_ref),
        data = PM_MB_train)
summary(PM_MB_trainLMER.3) # log(grain yeild) is a significant predictor of log(yielderror)
anova(PM_MB_trainLMER, PM_MB_trainLMER.3) # no significant difference between the models

# Lets try with Fungicide as a fixed effect
PM_MB_trainLMER.4 <-
   lmer(yield_error ~ `grain_yield.t.ha` + as.factor(fungicide_ai) +
           (1 | trial_ref),
        data = PM_MB_train)
summary(PM_MB_trainLMER.4)
anova(PM_MB_trainLMER, PM_MB_trainLMER.4) # no significant difference between the models

#log transforming the response or predictor variables did not improve the model therefore I will leave it untransformed
# I will be using the first model PM_MB_trainLMER for further analyses beyond this point

# Extract the model coefficients
paramA <-
   (summary(PM_MB_trainLMER)$coef)[2, 1] # Extract the overall mean slope to predict Yield error
InterC <-
   (summary(PM_MB_trainLMER)$coef)[1, 1] # Extract the overall mean intercept to predict Yield error
lmer.coef <-
   coef(PM_MB_trainLMER) # extracting the mean random intercept for each of trial variables

# plot of the mixed effect model, Black line shows the mean lmer regression line
ggplot(PM_MB_train) +
   geom_point(aes(y = yield_error, x = grain_yield.t.ha, colour = trial_ref)) +
   geom_abline(
      intercept = c(InterC, lmer.coef$trial_ref[, 1]),
      slope = c(paramA, lmer.coef$trial_ref[, 2]),
      size = 1,
      colour = c("Black", hue_pal()(16))
   ) +
   coord_cartesian(xlim = c(0, 3)) +
   theme_usq()
```

```{r na2Sv_formula}
for (i in NATrials$trial_ref) {
   #Sv <- (log(PM_MB_means[PM_MB_means$trial_ref == i,]$`grain_yield.t.ha`) - InterC)/ paramA  # parameter from when I had the predictor and response variable flipped

@@

   PM_MB_means[PM_MB_means$trial_ref == i,]$yield_error <- Sv
   PM_MB_means[PM_MB_means$trial_ref == i,]$y_error.type <-
      "SamplingVariance"
}
```

Let's look at the model without the trial mung1718/01, as it looks to be adding some skew.

```{r lmer_remove_mung1718-01}
# remove from mung1718/01 from training dataset
PM_MB_train.2 <-
   PM_MB_train[PM_MB_train$trial_ref != "mung1718/01",]

# Rerun the model
PM_MB_trainLMER.5 <- lmer(yield_error ~ `grain_yield.t.ha` +
                             (1 | trial_ref), data = PM_MB_train.2)
summary(PM_MB_trainLMER.5) # no significant effect of mean grain yield on yield error

# Extract the cooeficients
paramA <-
   (summary(PM_MB_trainLMER.5)$coef)[2, 1] # Extract the overall mean Slope to predict Yield error
InterC <-
   (summary(PM_MB_trainLMER.5)$coef)[1, 1] # Extract the overall mean intercept to predict Yield error
lmer.coef <-
   coef(PM_MB_trainLMER.5) # extracting the mean random intercept for each of trial variables

# plot the data with the predicted slopes overlayed
ggplot(PM_MB_train.2) +
   geom_point(aes(y = yield_error, x = grain_yield.t.ha, colour = trial_ref)) +
   geom_abline(
      intercept = c(InterC, lmer.coef$trial_ref[, 1]),
      slope = c(paramA, lmer.coef$trial_ref[, 2]),
      size = 1,
      colour = c("Black", hue_pal()(15))
   ) +
   coord_cartesian(ylim = c(0, 0.33)) +
   xlab("Grain Yield (t/ha)") +
   ylab("Yield Error") +
   scale_colour_discrete("Trial Reference") +
   theme_usq()
```

Just for kicks lets look at the linear regression model as a random effects model where `grain_yield.t.ha` is set as a random slope to the random intercept `trial_ref`.

The model fits better as shown by an ANOVA comparison. But how to impute from this model if mean variance for a trial is unknown...

```{r random_slope_model}
# Run a linear model with yield error as a fixed effect predictor and trial as a random intercept
PM_MB_trainLMERx <- lmer(yield_error ~ 1 +
                            (grain_yield.t.ha |
                                trial_ref), data = PM_MB_train)

anova(PM_MB_trainLMER, PM_MB_trainLMERx) # random slope model NOT significantly better # P = 0.6677

summary(PM_MB_trainLMERx)

InterC <-
   (summary(PM_MB_trainLMER)$coef)[1, 1] # Extract the overall mean intercept

lmer.coefx <- coef(PM_MB_trainLMERx)

# plot of the mixed effect model, Black line shows the mean lmer regression line
ggplot(PM_MB_train) +
   geom_point(aes(y = yield_error, x = grain_yield.t.ha, colour = trial_ref)) +
   geom_abline(
      intercept = lmer.coefx$trial_ref[, 2],
      slope = lmer.coefx$trial_ref[, 1],
      size = 1,
      colour = hue_pal()(16)
   ) +
   coord_cartesian(xlim = c(0, 3),
                   ylim = c(0, 1)) +
   xlab("Grain Yield (t/ha)") +
   ylab("Yield Error") +
   scale_colour_discrete("Trial Reference") +
   theme_usq()
```

After much deliberation I don't think this is possible to use the model with grain yield t/ha as a random slope. Even though we know the grain yields and the mean of the grain yields, we still can't predict the effect of the random intercept trial on the yield error.

I also re-ran the model without including the trial in which we used LSD to interpret the sampling variance and the model lost a lot of significance.

## Between trial variation

Emerson proposed I look at the between trial variation.

PM_MB_means.SV <-
   filter(PM_MB_means, y_error.type == "SamplingVariance")

PM_MB_means_T <- PM_MB_means %>%
   group_by(trial_ref) %>%
   summarise(
      trial_mean = mean(grain_yield.t.ha, na.rm = TRUE),
      BW_trial_variance = sd(grain_yield.t.ha, na.rm = TRUE) ^ 2
   )

PM_MB_means <- left_join(PM_MB_means, PM_MB_means_T, by = "trial_ref")

summary(lm(BW_trial_variance ~ trial_mean, data = PM_MB_means))
summary(lm(
   BW_trial_variance ~ trial_mean,
   data = subset(PM_MB_means, fungicide_ai == "tebuconazole")
))
summary(lm(
   BW_trial_variance ~ trial_mean,
   data = subset(PM_MB_means, fungicide_ai == "propiconazole")
))

plot(BW_trial_variance ~ trial_mean, data = PM_MB_means)
abline(-0.01356, 0.03076)

@@
